\documentclass[a4paper, oneside, final]{article}

\usepackage[utf8]{inputenc}

%\usepackage{scrpage2}
\usepackage{titlesec}
\usepackage{marvosym} 
\usepackage{tabularx,colortbl} 



\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
%\pagestyle{scrheadings}

\addtolength{\voffset}{-0.5in}
\addtolength{\textheight}{3cm}

\title{Curriculum Vitae}
\author{Pawel Sawicz}
\date{   } 

%\renewcommand{\headfont}{\normalfont\rmfamily\scshape}

%\cofoot{
%\addfontfeature{LetterSpace=5.0}\fontsize{10}{17}\selectfont 
%
%I hereby authorize you to process my personal data included in my job application for
%the needs of the recruitment process (in accordance with the Personnel Protection
%Act of 29.08.1997 no 133 position 883).
%}
\renewcommand*\rmdefault{iwona}

\begin{document}

\maketitle

%%Personal Information Section%%
\section{Personal Informations }
\begin{center}
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Telephone & \textbf{+44 079 403 287 80}\\
 E-mail & \textbf{pawel@sawicz.eu}\\
 Blog & \textbf{pawel.sawicz.eu}\\
 Github & \textbf{github.com/pawelsawicz}\\
\end{tabularx}
\end{center}
%%End Personal Information Section%%
%%Profile Section%%
\section{Profile}
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 & Engineering Lead specialising in distributed systems and building products.
 Crazy about learning new things, but balanced when taking a risk.
 In spare time trying to understand type theory and constructive logic.
 Heavily involved in .NET community, co-organizer virtual conference, 
 moreover attendee and speaker of several conferences around Europe. \\
\end{tabularx}
%%End Profile Section%%
%%Work Experiance Section%%
\section{Work Experience}
\begin{center}

 \begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
  Period & \textbf{January 2021 --- Present }\\
  Employer & \textbf{Checkout.com} \hfill London, United Kingdom\\
  Job Title & \textbf{Engineering Lead - Arundel Squad}\\
  &
	Leading a squad of 5 developers. Being responsible for mentoring, managing 
	and paving a technical vision for reconciliation product. Successfully delivered reconciliation product that decreased manual effort of 
	reconciling transactions from 6 working hours to 15 minutes 
	with a cover of 65 \% of Checkout transaction volume.
	
	Helping Checkout to scale world wide with right 
	reconciliation tools that will cover all world transactions.

	Technologies:
	\begin{itemize}
	\item DevOps (AWS, Terraform, Docker)
	\item Messaging (SQS, SNS, Kinesis), 
	\item Coding (.NET/C\#)
	\item Monitoring/Logging (Prometheus, DataDog, Grafana)
	\end{itemize}
	 \\
 \end{tabularx}
 \vspace{12pt} 

 \begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
  Period & \textbf{September 2019 --- January 2021 }\\
  Employer & \textbf{Checkout.com} \hfill London, United Kingdom\\
  Job Title & \textbf{Senior Software Engineer - FORT team}\\
  &
	Building reconciliation products for the finance department within Checkout.
	Working with the team on architecture design, mentoring peers, heavily involved in the recruitment process.
	Being involved in shaping team structure.

	Top projects:
	\begin{itemize}
	\item Transaction alerting product. Product that runs buissnes checks on all transactions (i.e does a transaction was successfully sent to clearing within T+1)
	\item Debtor rolling position. Reporting product showing how much money Checkout owns to card schemes (Visa/Mastercard)
	\end{itemize}


	Technologies:
	\begin{itemize}
	\item DevOps (AWS, Terraform, Docker)
	\item Messaging (SQS, SNS, Kinesis), 
	\item Coding (.NET/C\#)
	\item Monitoring/Logging (Prometheus, DataDog, Grafana)
	\end{itemize}
	\\
 \end{tabularx}
 \vspace{12pt}
 
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Period & \textbf{March 2016 --- August 2019 }\\
 Employer & \textbf{Zopa} \hfill London, United Kingdom\\
 Job Title & \textbf{Software Engineer}\\ 
	& Worked on the core part of Zopa business.
	 Being exposed to all parts of Zopa business (Bank, Borrowing, Lending).
	 Being involved and leading architectural decisions across the whole business.
	
	Top project:
	\begin{itemize}
	\item Rolling out new loan algorithm impacting 95\% of existing loan book (4.5bln pounds)
	\item Zopa Auto product, greenfield project that is adopted by the Car industry, revolutionising car loan industry (Adopted by all major players) est. market cap 10bln pounds.
	\item Enabled Zopa Bank launch by working on key projects.
	\item Involved in the recruitment process, being involved in around 200 interviews at various stages (code review, phone interview, face to face).
	\item Responsible for extracting microservices out of the monolith. 
 	\end{itemize}
	Technologies: CQRS, EventSourcing, DDD, Jenkins, Packer, Splunk\\
\end{tabularx}
\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Period & \textbf{July 2014 --- February 2016}\\
 Employer & \textbf{JustGiving} \hfill London, United Kingdom\\
 Job Title & \textbf{API Developer / Evangelist}\\ 
& Being involved in forming API team and shaping its form. I am very proud to have founded and grown the community arund the JG public api. I helped out and hosted events and international hackathons. To technical side of role belonged: creating architecture of API, maintaining and monitoring health of API, supporting customers in case of technical problems. Many contribution to core JustGiving codebase, re-factoring old parts of API, writing TDD. Overview of technologies: NancyFx, WebApi, Owin, ASP. MVC, Microservices, CQRS. Heavily worked in cloud enviroment, Amazon Web Services, used tools like : Raygun, Kibana, Chef, Vagrant, GO CD\\
\end{tabularx}
\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Period & \textbf{July 2013 --- June 2014}\\
 Employer & \textbf{Neurosys} \hfill Wroclaw, Poland\\
 Job Title & \textbf{Junior .NET Developer}\\ 
& Involved in maintaince and development of new features. Writing unit tests to cover fragile parts of the code. Worked as fronted and backend developer. Responsible for implementing RWD in two projects, worked with knockout and ASP.NET MVC/Web API\\
\end{tabularx}
\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Period & \textbf{June 2011 --- September 2011, August 2012 --- September 2012}\\
 Employer & \textbf{Chroma.pl} \hfill Zary, Poland\\
 Job Title & \textbf{Junior .NET Developer}\\
& Responsible for one major feature addon. Created unit test to cover code. Worked with ‘linq to excel‘ library. Prepared SQL queries. Created library that checks the e-mail, by RCPT protocol.\\
\end{tabularx}
\vspace{12pt}
\end{center}
%%End Work Experiance Section%%
%%Education Section%%
\section{Education}

\begin{center}
 
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Period & \textbf{October 2011 --- February 2015 }\\
 Degree & \textbf{Bachelor of Science}\\
 University & \textbf{Wroclaw University of Technology} \\
 Field &\textbf{Electronic \& Telecommunication}\\
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
 Period & \textbf{October 2018 --- January 2022 }\\
 Degree & \textbf{Master of Science}\\
 University & \textbf{University of Oxford} \\
 Field &\textbf{Computer Software Engineering}\\
\end{tabularx}
\vspace{12pt}
 
\end{center}

%%End Education Section%%
%%Skills Section%%

\section{Skills}
\begin{center}
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{4cm}X}
\textbf{Last three months} & \\
Frameworks & NancyFx,  ASP.NET MVC, WebApi\\
Databases & NHibernate,  MSSQL\\
Tools & TeamCity, Go CD, Chef, Vagrant, Terraform, Swagger, Raygun, Kibana\\
\end{tabularx}
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{4cm}X}
\textbf{Fundamental knowledge} & \\
Frameworks & .NET\\
Programming Languages & {C\#, JavaScript, SQL} \\
Tools & Git, SVN, Log2Console,   \\
Practise & Unit Tests, TDD, SOILD, Mutation Testing\\
Liblaries & jQuery, NUnit, FluenAssertions, TinyIoC, Automapper, NLog, RestSharp  \\
\end{tabularx}
\end{center}
%%End Skills Section%%
%%Activities Section%% %ToDo as list section!!!

\section{Activities}
\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
& \textbf{- Active memeber of .NET Group (PWr Wroclaw)}\\
& \textbf{- Imagine Cup participant (2012, 2013 editions)}\\
&  - 2012 edition - Tourist Guide \\
& Web application which provide information about travelling and sightseeing. \\
& - 2013 edition - BusCatcher \\
& Windows Phone 7 application which use external API to gather information about current position of public transport vehicles \\
& \textbf{- dotNetConfPL co-organizer}\\
& First polish virtual conference about .net - 200 attendees\\
\end{tabularx}

%%End Activities Section%%

%%Languages Section%%
\section{Languages}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{4cm}X}
English & \textbf{Fluent}\\
Polish & \textbf{Native}\\
\end{tabularx}

\end{document}
